prolfqua&colon; A Comprehensive R-package for Proteomics Differential Expression Analysis

### 2022-09-22 inst/MyArticle/paper.Rmd
adding to bibliography,
fix caption

(ref:FDRfdp) Panel A - Number of estimated contrasts for each modeling method (higher is better). Panel B - Partial area under the ROC curve at $10\%$ FPR ($pAUC_10$) for all contrasts and three different statistics: the difference among groups, the scaled $p$-value (sign(diff) $\cdot$ p.value) and the $t$-statistics (higher is better). The red line indicates the average area under the curve of all methods.  Panel C - Plots the false discovery proportion ($FDP$) as a function of the $FDR$. Ideally, the $FDR$ should be equal to the $FDP$. Therefore larger distances from the diagonal are worse.

@@

## Benchmark

>>>>

(ref:FDRfdp) Panel A - Number of estimated contrasts for each modeling method (higher is better). Panel B - Partial area under the ROC curve at $10\%$ FPR ($pAUC_{10}$) for all contrasts and three different statistics: the difference among groups (diff - Panel B left), the scaled $p$-value (sign(diff) $\cdot$ p.value) (scaled.p.value - Panel B center) and the $t$-statistics (statistic - Panel B right), where a higher pAUC is better. The red line indicates the average area under the curve of all methods.  Panel C - Plots the false discovery proportion ($FDP$) as a function of the $FDR$. Ideally, the $FDR$ should be equal to the $FDP$. Therefore larger distances from the diagonal are worse.

@@

## Benchmark Code
